Adapting Duplicate Filters to a Sliding Window Context

### 2020-03-26 qhtv2.tex
wip

We begin with the following, ideal problem: 
\begin{definition}[Duplicate detection problem, DDP] Given a stream $E_n = (e_1, e_2, \dotsc, e_n)$ and a \enquote{new} item $e^\star$, find whether $e^\star \in E_n$.\footnote{
	We do not consider here \emph{fuzzy} detection approaches \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient} that study situations where $e^\star$ belongs to $E_n$ when there exists a \enquote{similar enough} element in the stream.
}
	At every time increment, the new item is added to the stream, i.e., $E_{n+1} = E_n \mid e^\star$ where $\mid$ denotes concatenation. 
\end{definition}
Instances of this problem abound in computer science, with applications in file system indexation, database queries, network load balancing, network management \cite{10.5555/647912.740658}, in credit card fraud detection \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094}, etc. A discussion about algorithms on large data streams can be found in \cite{10.1145/776985.776986}.

In practice, additional constraints exist that we can capture with the following definition:
\begin{definition}[DDP with bounded memory]
	At every time step $n$, given $e^{\star}$ and a current state (dependent on history) of at most $M$ bits, solve the DDP for $E_n$ and $e^{\star}$.
\end{definition}
%Even when the stream is bounded, i.e. $\lim_{n\to\infty}|E_n| < \infty$, it may be impractical to perform a complete lookup and approximate solutions are desirable. 
One can prove \cite[Theorem 2.1]{10.1145/3297280.3297335} that perfect detection of duplicates in a stream with $U$ possible values requires $U$ bits of memory: even for modest situations (e.g. 64-bit nonces, corresponding to $2^{64}$ possible values) this is quickly impractical. As a result, we need a further relaxation of the DDP that allows for errors: 
\begin{definition}[Approximate DDP with bounded memory]
	Solve the DDP using at most $M$ bits of memory, with at most $\epsilon < 1/2$ mispredictions.\footnote{Given a classifier with $\epsilon > 1/2$, we obtain a classifier with $\epsilon < 1/2$ by reversing its output.} 
\end{definition}
Approximate duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the ElGamal \cite{10.1007/3-540-39568-7_2} or ECDSA signatures. Other uses include improvements over caches \cite{4484874}, duplicate clicks \cite{10.1145/1060745.1060753}, and others.

@@

Several algorithms have been proposed to solve the DDP, but
they \emph{all} face a phenomenon called \enquote{saturation} on large data streams \cite{10.1145/3297280.3297335}. Essentially, when saturation happens the algorithm performs no better than at random. This is problematic on two grounds: it makes the comparison of several algorithms difficult (since they all asymptotically behave in that fashion), and the unavoidable saturation ruins any particular design's merits.

\subsection{Contributions}
To circumvent the aforementioned limitations, we introduce a variant of the DDP \emph{over a sliding window}, which enables the design of filters that avoids the saturation issue altogether (Section~\ref{sec:dudefisa}). We provide explicit upper bounds for the amount of memory necessary to solve this problem, and corresponding constructions.

We then introduce the \emph{queuing construction}, a generic approach to build windowed-DDP-friendly filters from existing filters (Sections~\ref{sec:queue} and \ref{sec:subfilter-select}). We analyse the queuing construction's error rates and parameters (Section~\ref{sec:optimising}), which are confirmed by benchmarks (Section~\ref{sec:bench}).

Finally, we provide an analysis of the queuing construction's resistance to adversarial streams (Section~\ref{sec:adversarial}).

\subsection{Related work}\label{sub:related}
\cite{10.1145/1060745.1060753} studies a structure aking to the counting Bloom filter, in a \enquote{landmark-} and \enquote{jumping-} sliding window setting. Despite the name, these are different from the sliding window discussed in this paper.

Closer to our work, the idea of using subfilters may be found in the A2 filter's design \cite{Yoo10}. The A2 is built from two Bloom filters, a situation which we generalise and analyse generically in this paper.

\todo[continuer]

\subsection{Organisation}

@@

\begin{definition}[Duplicate and unseen element]
Let $E = (e_1, e_2, \dotsc)$ be a stream over $\Gamma$. Some element $e_j \in E$ is called a \emph{duplicate} if and only if there exists $i < j$ such that $e_i = e_j$. In that case we write $e_j \dup E$. Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notdup E$.
\end{definition}

@@

We will usually consider the situations where the available memory is too small for perfect detection, i.e., $|\mathcal S| \ll |\Gamma|$.

\begin{definition}[False positive, false negative]
	Let $e \dup E$ (resp. $e \notdup E$) and $\mathcal F$ be a filter. We say that $e$ is a \emph{false positive} (resp. \emph{false negative}) when $\mathcal F.\mathsf{Detect}(e) = \DUPLICATE$ (resp. $\UNSEEN$).
\end{definition}

\begin{definition}[False positive rate, false negative rate]
	Let $E$ be a stream, $\mathcal F$ be a filter. The \emph{false positive rate} (resp. \emph{false negative rate}) of $\mathcal F$ over the first $i < n$ elements, denoted $\FPR_i$ (resp. $\FNR_i$), is defined as the ratio of false positives divided over the number of unseen elements in $(e_1, \dotsc, e_i)\subset E$ (resp. the ratio of false negative divided by the number of duplicate elements in that subset).
\end{definition}

However, it is more practical to work with another value, namely, the probability that after $m$ insertions, the element $e^\star$ is a false positive (resp. false negative).

\begin{definition}[Probability of false positive, of false negative]
	\label{def:pfp-pfn}
	Let $E = (e_1, \dotsc)$ be a stream, $\mathcal F$ be a filter. The \emph{probability of false positive} (resp. \emph{probability of false negative}) of $\mathcal F$ after $i$ elements, denoted $\FP_i$ (resp. $\FN_i$), is defined as the probability that $e_{i+1}$ is a false positive (resp. false negative).
\end{definition}

One can observe that $\FPR_n = \frac{1}{n}\sum_{i=1}^n \FP_i$, and similarly for $\FNR_n$.

\subsection{Filter Saturation and Sliding Windows}\label{sec:filsat}
Unfortunately, efficient duplicate detection over an infinite stream has been identified as an unsolvable problem \cite{10.1145/3297280.3297335}. As a matter of fact, as the number of bits of information of the stream grow to infinity, the filter can only remember an ever diminishing proportion of those bits, eventually having no advantage compared to a filter answering randomly.

In other terms, any DDF is asymptotically as good as a random guess:
	\begin{theorem}[\cite{10.1145/3297280.3297335}]\label{thm:sat_u}
	Let $\FNR_\infty$ and $\FPR_\infty$ be the asymptotic false negative and false positive rates of a filter of $M$ bits of memory (i.e. the FNR and FPR on a stream of size going to infinity).

	If $|\Gamma| \gg M$, then $\FNR_\infty + \FPR_\infty = 1$, which characterises random filters (i.e. filters answering randomly to any query).
\end{theorem}

One way out of this situation is to lower our expectations and work on a sliding window:

\begin{definition}[Sliding window DDP]
	Given a stream $E_n$ of fixed size $w$, with $E_n = (e_{n-w+1}, \dotsc, e_n)$ and an item $e^\star$, find whether $e^\star \in E_n$.
\end{definition}

We therefore introduce new definitions suited to that setting:

@@

\subsection{Bounds on the Sliding Window DDP}\label{sub:opt_solutions}

@@

\begin{theorem}
	For $M \geq w (\log_2(w) + 2\log_2(|\Gamma|))$, the sliding window DDP can be solved exactly (with no errors) in constant time.
\end{theorem}

@@

	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact account of how many times each element was present in the sliding window.
\end{proof}
The dependence on $\log_2 |\Gamma|$ can be dropped, at the cost of allowing 
errors:
\begin{theorem}
	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the sliding window DDP can be solved with almost no error using $M$ bits of memory.

@@

When $\log_2|\Gamma| > 5 \log_2 w$ this DDF outperforms the naïve strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w \log_2|\Gamma|$ bits of memory.}, both in terms of time and memory, at the cost of a minimal error. When $\log_2|\Gamma| > 2 \log_2 w$, it outperforms the exact solution described sooner in terms of memory.

Hence, very good solutions for situations where $M \approx 5w\log_2 w$ already exist, but efficient solutions and lower bounds on the error rates for smaller amounts of memory are still to be found.

\subsection{DDP vs Sliding Window DDP}
The sliding window variant of DDP may seem to be a slight weakening of the original problem. Remarkably, it turns out that DDFs which perform well for the DDP do rather poorly for the sliding window DDP. A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF) \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}. The structure proposed in \cite{10.1145/1060745.1060753} is not suited to either sliding window or no sliding window DDP, as they work on what they call `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.

\todo[Expliquer ?]

@@

If solving the equation for individual cases is 
%\end{equation*}

>>>>

We study the following problem: 
\begin{definition}[Duplicate detection problem on a sliding window, wDDP] Given a stream $E_n = (e_1, e_2, \dotsc, e_n)$, a sliding window size $w$ and a \enquote{new} item $e^\star$, find whether $e^\star$ is also present in the last $w$ elements of the stream, ie., whether $e^\star \in \{e_{n-w+1}, \dotsc, e_n\}$.
At every time increment, the new item is added to the stream, i.e., $E_{n+1} = E_n \mid e^\star$ where $\mid$ denotes concatenation. 
\end{definition}
Instances of this problem abound in computer science, with applications in file system indexation, database queries, network load balancing, network management \cite{10.5555/647912.740658}, in credit card fraud detection \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094}, etc. A discussion about algorithms on large data streams can be found in \cite{10.1145/776985.776986}.

In practice, additional constraints exist that we can capture with the following definition:
\begin{definition}[wDDP with bounded memory]
	At every time step $n$, given $e^{\star}$ and a current state (dependent on history) of at most $M$ bits, solve the wDDP for $E_n$ and $e^{\star}$.
\end{definition}
%Even when the stream is bounded, i.e. $\lim_{n\to\infty}|E_n| < \infty$, it may be impractical to perform a complete lookup and approximate solutions are desirable. 
One can prove \cite[Theorem 2.1]{10.1145/3297280.3297335} that perfect detection of duplicates in a stream with $U$ possible values requires $U$ bits of memory: even for modest situations (e.g. 64-bit nonces, corresponding to $2^{64}$ possible values) this is quickly impractical. As a result, we need a further relaxation of the DDP that allows for errors: 
\begin{definition}[Approximate wDDP with bounded memory]
	Solve the wDDP using at most $M$ bits of memory, with at most $\epsilon < 1/2$ mispredictions.\footnote{Given a classifier with $\epsilon > 1/2$, we obtain a classifier with $\epsilon < 1/2$ by reversing its output.} 
\end{definition}
Approximate duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the ElGamal \cite{10.1007/3-540-39568-7_2} or ECDSA signatures. Other uses include improvements over caches \cite{4484874}, duplicate clicks \cite{10.1145/1060745.1060753}, and others.

@@

We observe that in the litterature, there exists a similar problem, which we call DDP, and which does not make use of any sliding window. For instance, in DDP on a stream $E_n$ the problem is to find whether $e^\star \in E_n$. However, even though several algorithms have been proposed for this problem (\cite{Den06,10.1145/3297280.3297335,Dut13} and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}), they \emph{all} face a phenomenon called \enquote{saturation} on large data streams \cite{10.1145/3297280.3297335}. This phenomenon is not related to the filter, but rater to the nature of the DDP itself. Essentially, when saturation happens the algorithm performs no better than at random. This is problematic on two grounds: it makes the comparison of several algorithms difficult (since they all asymptotically behave in that fashion), and the unavoidable saturation ruins any particular design's merits.

\subsection{Contributions}
%To circumvent the aforementioned limitations, we introduce a variant of the DDP \emph{over a sliding window}, which enables the design of filters that avoids the saturation issue altogether (Section~\ref{sec:dudefisa}). We provide explicit upper bounds for the amount of memory necessary to solve this problem, and corresponding constructions.
%
%We then introduce the \emph{queuing construction}, a generic approach to build windowed-DDP-friendly filters from existing filters (Sections~\ref{sec:queue} and \ref{sec:subfilter-select}). We analyse the queuing construction's error rates and parameters (Section~\ref{sec:optimising}), which are confirmed by benchmarks (Section~\ref{sec:bench}). 
%
%Finally, we provide an analysis of the queuing construction's resistance to adversarial streams (Section~\ref{sec:adversarial}).
\todo

\subsection{Related work}\label{sub:related}
The notion of sliding window was, as far as we know, first introduced in \cite{10.1145/1060745.1060753}. However, the definition is not the one we use, as several variations exist such as \cite{shtul2020agepartitioned}. Instead, the wDDP formulation we used was already introduced in \cite{Yoo10,She08}. Both of these papers propose an algorithm for the wDDP.

Closer to our work, the idea of using subfilters can be found in the A2 filter's design \cite{Yoo10} and a variation of our idea can be found in a very recent construction, on a slightly different DDP formulation \cite{shtul2020agepartitioned}. The A2 is built from two Bloom filters, a situation which we generalise and analyse generically in this paper. Similarly, the solution in \cite{shtul2020agepartitioned} only works with Bloom Filters.

\subsection{Organisation}
\todo

@@

@@

We usually consider the situations where the available memory is too small for perfect detection, i.e., $|\mathcal S| \ll |\Gamma|$. Otherwise, if $|\mathcal S| = |\Gamma|$ then solutions in constant time and without errors exist \cite{10.1145/3297280.3297335}.

@@

%\begin{definition}[Duplicate and unseen element]
%Let $E = (e_1, e_2, \dotsc)$ be a stream over $\Gamma$. Some element $e_j \in E$ is called a \emph{duplicate} if and only if there exists $i < j$ such that $e_i = e_j$. In that case we write $e_j \dup E$. Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notdup E$.
%\end{definition}
%

%
%\begin{definition}[False positive, false negative]
%	Let $e \dup E$ (resp. $e \notdup E$) and $\mathcal F$ be a filter. We say that $e$ is a \emph{false positive} (resp. \emph{false negative}) when $\mathcal F.\mathsf{Detect}(e) = \DUPLICATE$ (resp. $\UNSEEN$).
%\end{definition}
%
%\begin{definition}[False positive rate, false negative rate]
%	Let $E$ be a stream, $\mathcal F$ be a filter. The \emph{false positive rate} (resp. \emph{false negative rate}) of $\mathcal F$ over the first $i < n$ elements, denoted $\FPR_i$ (resp. $\FNR_i$), is defined as the ratio of false positives divided over the number of unseen elements in $(e_1, \dotsc, e_i)\subset E$ (resp. the ratio of false negative divided by the number of duplicate elements in that subset).
%\end{definition}
%
%However, it is more practical to work with another value, namely, the probability that after $m$ insertions, the element $e^\star$ is a false positive (resp. false negative). 
%
%\begin{definition}[Probability of false positive, of false negative]
%	\label{def:pfp-pfn}
%	Let $E = (e_1, \dotsc)$ be a stream, $\mathcal F$ be a filter. The \emph{probability of false positive} (resp. \emph{probability of false negative}) of $\mathcal F$ after $i$ elements, denoted $\FP_i$ (resp. $\FN_i$), is defined as the probability that $e_{i+1}$ is a false positive (resp. false negative).
%\end{definition}

One can observe that $\FPR^w_n = \frac{1}{n}\sum_{i=1}^n \FP^w_i$, and similarly for $\FNR^w_n$.

%\subsection{Filter Saturation and Sliding Windows}\label{sec:filsat}
%Unfortunately, efficient duplicate detection over an infinite stream has been identified as an unsolvable problem \cite{10.1145/3297280.3297335}. As a matter of fact, as the number of bits of information of the stream grow to infinity, the filter can only remember an ever diminishing proportion of those bits, eventually having no advantage compared to a filter answering randomly.
%
%In other terms, any DDF is asymptotically as good as a random guess:
%	\begin{theorem}[\cite{10.1145/3297280.3297335}]\label{thm:sat_u}
%	Let $\FNR_\infty$ and $\FPR_\infty$ be the asymptotic false negative and false positive rates of a filter of $M$ bits of memory (i.e. the FNR and FPR on a stream of size going to infinity).
%	
%	If $|\Gamma| \gg M$, then $\FNR_\infty + \FPR_\infty = 1$, which characterises random filters (i.e. filters answering randomly to any query).
%\end{theorem}
%
%One way out of this situation is to lower our expectations and work on a sliding window:
%
%\begin{definition}[Sliding window DDP]
%	Given a stream $E_n$ of fixed size $w$, with $E_n = (e_{n-w+1}, \dotsc, e_n)$ and an item $e^\star$, find whether $e^\star \in E_n$.
%\end{definition} 
%
%We therefore introduce new definitions suited to that setting:
%
%\begin{definition}[Duplicate element, unseen element over a sliding window]
%	Let $E = (e_1, e_2, \dotsc)$ be a stream over $\Gamma$, let $w\in \mathbb N$, an element $e_j \in E$ is called a \emph{duplicate} in $E$ over the sliding window of size $w$ if and only if there exists $j$ such that $j - w \leq i < j$  and $e_i = e_j$. In this case we write $e_j \wdup E$. Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notwdup E$.
%\end{definition}
%
%\begin{definition}[False positive, false negative over a sliding window]
%	Let $w \in \mathbb N$, $e \notwdup E$ (resp. $e \wdup E$) and let $\mathcal F$ be a DDF. We say that $e$ is a \emph{false positive} (resp. \emph{false negative}) over $w$ if $\mathsf{Detect}(e) = \DUPLICATE$ (resp. $\UNSEEN$).
%\end{definition}
%
%\begin{definition}[False positive rate, false negative rate over a sliding window]
%	Let $E$ be a stream, $\mathcal F$ be a DDF, $w \in \mathbb N$. The \emph{false positive} (resp. \emph{false negative}) rate of $\mathcal F$ over the first $i < n$ elements and the sliding window $w$, noted $\FPR^w_i$ (resp. $\FNR^w_i$), is defined as the number of false positives over $w$ divided by the number of unseen elements in $E$ over $w$ (resp. the number of false negative over $w$ divided by the number of duplicate elements over $w$).
%\end{definition}

\subsection{DDP vs wDDP}
As noted before, some DDF were defined on the DDP, thus not offering a simple analysis of their error rates on the wDDP.

The sliding window variant of DDP may seem to be a slight weakening of the original problem.% Remarkably, it turns out that DDFs which perform well for the DDP do rather poorly for the sliding window DDP.
A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF) \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}. The structure proposed in \cite{10.1145/1060745.1060753} is not suited to either sliding window or no sliding window DDP, as they work on what they call `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.

\section{Optimal and Approximate Solutions}
\subsection{Optimal wDDF}\label{sub:opt_solutions}

@@

\begin{theorem}
	For $M \geq w (\log_2(w) + 2\log_2(|\Gamma|))$, the wDDP can be solved exactly (with no errors) in constant time.
\end{theorem}

@@

	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact account of how many times each element was present in the sliding window.
\end{proof}

\subsection{Approximate Optimal wDDF}
In the previous section, the optimal filter requires to know the size of $\Gamma$, which might be unknown, unbounded or simply too big for practical applications. 
The dependence on $\log_2 |\Gamma|$ can be dropped, at the cost of allowing errors.

\begin{theorem}\label{thm:SHF}
	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the wDDP can be solved with almost no error using $M$ bits of memory.

@@

When $\log_2|\Gamma| > 2 \log_2 w$ this DDF outperforms the naïve strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w \log_2|\Gamma|$ bits of memory.}, both in terms of time and memory, at the cost of a minimal error. When $\log_2|\Gamma| > 2 \log_2 w$, it outperforms the exact solution described sooner in terms of memory.

\section{Short Hash Filter}
\subsection{Short Hash Filter Algorithm}
The approximate filter we described uses hashes of size $2\log_2(w)$ for a given sliding window $w$. However, this hash size is arbitrary, and while it guarantees a very low error rate, it can be changed. More importantly, in some practical cases the maximal amount of available memory is fixed beforehand. Fixing the memory is also more practical for benchmarking various data structures, as it gives the guarantee that all filters operate under the same conditions.

This gives us the Short Hash Filter (SHF), described in Algorithm~\ref{alg:SHF}.

\begin{algorithm}[]
	\caption{SHF Setup, Lookup and Insert}\label{alg:SHF}

	\begin{algorithmic}[1]
		\Function{Setup}{$\mathcal M, w$}
		\Comment $M$ is the available memory, $w$ the size of the sliding window
		\State $h \gets$ hash function of codomain size $\lfloor \frac M{2w} - \frac 12 \log_2 w \rfloor$
		\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
		\State $D \gets \emptyset$ \Comment $D$ is a dictionary $h$ => counter (of max value $w$)

		\State\Return filter
		\EndFunction 
		\item[]
	\end{algorithmic}

	\begin{algorithmic}[1]
	\Function{Lookup}{$e$}
		\If{$D[h(e)] > 0$}
		\State \Return \DUPLICATE
		\EndIf
		\State \Return \UNSEEN
	\EndFunction
	\item[]
	\end{algorithmic}

	\begin{algorithmic}[1]
	\Function{Insert}{$e$}
		\State $Q.\mathsf{Push\_Front}(h(e))$
		\State $D[h(e)]$++

		\If{$Q.\mathsf{length}() > w$}
			\State $h' \gets Q.\mathsf{Pop\_back}()$
			\State $D[h']$-{}-
			\If{$D[h'] = 0$}
				\State Erase key $D[h']$
			\EndIf
		\EndIf
	\EndFunction
	\end{algorithmic}
\end{algorithm}

\subsection{Compact Short Hash Filter}
For the sake of completeness, we also introduce the Compact Short Hash Filter, which is very similar to the Short Hash Filter, but does not use any dictionnary. Hence, the filter is much slower (complexity of $O(w)$), but also has fewer errors since there is more place for the queue.

A quick description of the Compact Short Hash Filter (CSHF) is given in Algorithm~\ref{alg:CSHF}.

\begin{algorithm}[]
	\caption{CSHF, Lookup and Insert}\label{alg:CSHF}

	\begin{algorithmic}[1]
		\Function{Setup}{$\mathcal M, w$}
		\Comment $M$ is the available memory, $w$ the size of the sliding window
		\State $h \gets$ hash function of codomain size $\lfloor \frac Mw \rfloor$
		\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
		\State\Return filter
		\EndFunction 
		\item[]
	\end{algorithmic}

	\begin{algorithmic}[1]
		\Function{Lookup}{$e$}
		\State \Return $h(e) \in Q$ 
		\EndFunction
		\item[]
	\end{algorithmic}

	\begin{algorithmic}[1]
		\Function{Insert}{$e$}
		\Comment Same as SHF, but removing all instructions about its dictionnary $D$.
		\EndFunction
	\end{algorithmic}
\end{algorithm}

\subsection{Error Rates}
\begin{theorem}
	Let $w \in \mathbb N$. Let $M \in \mathbb N$ be the available memory size. Let $\FN^w_{SHF}$ be the probability of false negative of an SHF with these parameters. We similarly define $\FP^w_{SHF}$, $\FN^w_{CSHF}$, $\FP^w_{CSHF}$
	Both SHF and QSHF have $\FN^w = 0$.

	Furthermore we have $\FP_{SHF}^w = 1 - \left(1 - \sqrt{w2^{-M/w}}\right)^w$ and $\FP_{CSHF}^w = 1 - \left(1 - 2^{-M/w}\right)^w$.
\end{theorem}

\begin{proof}
	This is an immediate adaptation of the proof from Theorem~\ref{thm:SHF}. An SHF has fingerprints of size $h = \frac M{2w} - \frac 12 \log_2 w$, while a CSHF has fingerprints of size $h' = \frac Mw$.
\end{proof}

It can be noted that a CSHF of size $M$ has the same error rate than an SHF of size $(2 + \frac {\log_2 w}h)M$.
\subsection{Saturation}
When benchmarking both structures, it appears they saturate very quickly when changing $w$: in other words, most SHF will either have an error rate of $0$ or $1$.

For instance, we benchmarked the performance of CSHF and SHF with a memory $M=100000$, on a stream of size 1 000 000 consisting of uniformly random elements from an alphabet of size $2^{18}$. Results are given in Figure~\ref{fig:shorts}.

\begin{figure}
	\input{graphs/bench_shorts.tex}
	\caption{Error rates of SHFs and CSHFs of $100000$ bits, for various $w$.}\label{fig:shorts}
\end{figure}

More specifically, \todo[Trouver la formule pour laquelle CSHF sature à 50\% ou quelque chose du genre]

@@

If solving the equation for individual cases is doable, it however does not seem possible to derive a generic formula.
%\end{equation*}
